\chapter{Background}
STEM education became mre and more important since the AI boom. Many countries, including Hong Kong, have added STEM education as a part of their curriculum for kids. Yet, we have noticed that the common coding approach is used to teach students how to code in Hong Kong. However, coding has no pictures, nor much interaction i it. So this might not be attractive to young kids and cause them to have a low incentive and motivation to learn. Therefore we need a new way to program software, so that it is visualized and fun for the kids to use and learn programming from it.

Moreover, computers and smart gadgets is an indivisilbe part of our life now. More and more people devouted themselves into this area to provide different software and applications to enrich our daily life. However, many of these are start-uppers, and they may have a good idea, but they may not be able to express it and actualize it. Therefore, an easier way for people to create a software using public source codes is needed to decrease the cost and ease some of the difficulties of creating softwares.

Therefore, a new platform is needed to help beginners to write their software, and let them learn programming. Our project visualizes source codes into different blocks of code, so that programming beginners can understand the logic and syntax of the language. Programming by using different blocks of code can also allow programmers to use written code to create the software they need at ease. This way will also decrease the cost creating software for start-uppers.
