  \chapter{Introduction}
  \section{Project Overview}
  We are going to develop an online integrated development environment(IDE) which allows users to code by draging and dropping different blocks of code to form a program, instead of typing. It is an IDE developed for users without previous experiences in coding to learn the basic of coding.
  \section{Objective}
  STEM education is being more and more popular all over the world. However, we noticed that using common coding approach to teach programming may not be interesting and easy for young beginners to learn programming. This may hinder the learning progress of them.
  In order to enhance the learning progress and increase their incentive to learn, we believe a new paradigm should be introduced to replace coding. Inspired by how LEGO\textsuperscript{\textregistered} Mindstorms\textsuperscript{\textregistered} programs, we believe a visualized drag and drop online programming platform will be more suitable to educational purpose when aiming at these young kids.\par~

  We believe it is also an useful tool for rapid prototyping. Startupers without programming knowledge can use this programming IDE to start programming their software and applications with a lower difficulty. We also hope that this online IDE will also let programmers prototype their product at ease using pre-built function blocks in our online IDE. And this can also increase the reuse rate of code in software.\par~

  The Code Block Online IDE shall be a good platform for students to learn the basics of programming and a tool for programmers to rapid prototype their software.
  \section{Expected Customers and Market}
  We expected teachers, students and programmers will use our service.

  ~

  STEM education is promoted all over the world. Teachers can use Code Block Online IDE to teach programming in a more visualized way. So that students can understand the programming logic more easily. A visualized and interactive programming methodology instead of the common text-based codes should also increase students' interests in the lesson, so they will be more focused thus learn better. For students, a visualized programming IDE will lower their learning cost. And our online IDE being more colorful, can also increase their incentive to learn programming with our service.

  ~

  For programmers, our service will help them reduce their time needed in prototyping their product. We allow uploading written codes to our server and modulize them. And with some other objects and functions written by us, will shorten the time needed to develope a software by using different pre-made parts readily available.
  \section{System Features}
